NFL Draft Analysis

### 2020-05-12 draft_analysis.Rmd
Reformatted headings
Delete unnecessary columns

# Creating our Model

@@

# Testing against 2017-2019 data

@@

test_df <- merge(test_df, predictions, by = "row.names", all.x = FALSE, all.y = FALSE)
test_df$No.x <- NULL

@@

# Predicting the 2020 Rookie Offensive MVP

@@

df_2020 <- merge(df_2020, predictions, by = "row.names", all.x = FALSE, all.y = FALSE)
df_2020$No.x <- NULL

>>>>

## Creating our Model

@@

## Testing against 2017-2019 data

@@

test_df <- merge(test_df, predictions, by = "row.names", all.x = FALSE, all.y = FALSE)
test_df$No.x <- NULL
test_df$Row.names <- NULL

@@

## Predicting the 2020 Rookie Offensive MVP

@@

df_2020 <- merge(df_2020, predictions, by = "row.names", all.x = FALSE, all.y = FALSE)
df_2020$No.x <- NULL
df_2020$Row.names <- NULL
